\documentclass[12pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{longtable}
\usepackage{hyperref}
\usepackage{titling}
\usepackage{setspace}
\usepackage{array}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{amssymb}


\setlength{\droptitle}{-5em} % Move title up

\pagestyle{fancy}
\fancyhf{}
\lhead{HackMerced Bank --- Diamond Reserve Credit Card}
\rhead{\thepage}

\begin{document}

\title{\textbf{HackMerced Bank --- Diamond Reserve Credit Card Application}}
\author{}
\date{\today}
\maketitle

\thispagestyle{empty}

\begin{center}
\textbf{Application Number:} \underline{\hspace{2in}} \hspace{1cm}
\textbf{Issue Date:} \underline{\hspace{1.5in}}
\end{center}

\vspace{1cm}

\section*{Section I: Personal Information}
\noindent\textbf{Full Legal Name:} \\[1ex]
\textbf{Date of Birth (MM/DD/YYYY):} \\[1ex]
\textbf{Social Security Number (or equivalent):} \\[1ex]
\textbf{Residential Address:}\\
\quad Street: \\[1ex]
\quad City:  \quad State/Province:  \quad Zip/Postal Code: \\[1ex]
\quad Country: \\[2ex]
\textbf{Mailing Address (if different):}\\
\quad Street: \\[1ex]
\quad City:  \quad State/Province:  \quad Zip/Postal Code: \\[1ex]
\quad Country: \\[2ex]
\textbf{Contact Information:}\\[1ex]
\quad \textbf{Phone Number:} \\[1ex]
\quad \textbf{Email Address:} \\[2ex]

\section*{Section II: Financial Information}
\noindent\textbf{Employment Status:}\\[1ex]
\hspace{0.5cm} $\square$ Employed \hspace{1cm} $\square$ Self-Employed \hspace{1cm} $\square$ Unemployed \hspace{1cm} $\square$ Student \hspace{1cm} $\square$ Retired\\[2ex]
\textbf{Employer/Business Name:} \\[2ex]
\textbf{Annual Gross Income:} \\[2ex]
\textbf{Other Income (if applicable):} \\[2ex]
\textbf{Current Bank(s) and Account Types:} \\[2ex]
\textbf{Credit Score (Optional):} \\[2ex]

\section*{Section III: Credit Card Details}
\noindent\textbf{Card Type Selected:} \textbf{Diamond Reserve}\\[1ex]
\textbf{Desired Credit Limit:} \\[2ex]
\textbf{Preferred Billing Cycle:} \hspace{0.5cm} $\square$ 30-Day \hspace{1cm} $\square$ 60-Day\\[2ex]
\textbf{Payment Due Date Preference (MM/DD):} \\[2ex]
\textbf{Additional Cardholder(s):} \hspace{0.5cm} $\square$ Yes \hspace{1cm} $\square$ No\\[1ex]
\textit{(If yes, please attach supplementary information.)}

\section*{Section IV: Legal Authorization \& Consent}
\noindent By signing below, you certify that the information provided is accurate and complete. You authorize HackMerced Bank to verify your credit and financial history, and you agree to abide by all the terms and conditions specified herein.
\begin{itemize}[leftmargin=1.5cm]
    \item[$\square$] \textbf{I agree to the Terms and Conditions.}
\end{itemize}

\newpage

\section*{Section V: Terms and Conditions}
\begin{spacing}{1.1}
\textbf{1. Introduction}\\[1ex]
These Terms and Conditions govern your use of the Diamond Reserve credit card issued by HackMerced Bank. By applying, you acknowledge that you have read, understood, and agree to all provisions of this agreement. This document is legally binding and supersedes all prior communications, representations, or agreements, whether verbal or written.

\vspace{1em}
\textbf{2. Eligibility}\\[1ex]
Applicants must be at least 18 years of age and legally capable of entering into a binding contract. All applications are subject to verification, including identity, income, and creditworthiness. Incomplete or inaccurate information may result in application rejection or termination of account privileges.

\vspace{1em}
\textbf{3. Credit Limit, Fees, and Charges}\\[1ex]
\begin{itemize}
    \item The credit limit is determined based on your creditworthiness and may be adjusted at HackMerced Bank’s discretion.
    \item \textbf{Fees:} An annual fee, late payment fee, over-limit fee, returned payment fee, and any additional fees as specified in the account agreement may apply. Detailed fee schedules will be provided upon account activation.
    \item All fees and charges are subject to change with a 30-day notice to cardholders.
\end{itemize}

\vspace{1em}
\textbf{4. Interest Rates and Payment Terms}\\[1ex]
\begin{enumerate}[label*=\arabic*.]
    \item A grace period is provided for new purchases. Interest will accrue on any carried balance after the grace period, calculated at the Annual Percentage Rate (APR) specified on your statement.
    \item Minimum monthly payments are required. Failure to make timely payments may incur additional fees, increased interest rates, and may adversely affect your credit rating.
    \item Payment allocation shall be made as per the bank’s standard practices and in accordance with prevailing regulations.
\end{enumerate}

\vspace{1em}
\textbf{5. Rewards and Benefits Program}\\[1ex]
\begin{itemize}
    \item \textbf{Rewards Accrual:} Cardholders earn reward points for every eligible purchase as described in Section VI. Terms for bonus points and milestone achievements are subject to periodic review.
    \item \textbf{Redemption:} Points may be redeemed for travel, merchandise, statement credits, or cash back. The conversion rate and redemption options are subject to change without notice.
    \item \textbf{Limitations:} Rewards points are non-transferable, non-refundable, and have no cash value unless redeemed through approved channels.
\end{itemize}

\vspace{1em}
\textbf{6. Cardholder Responsibilities and Liability}\\[1ex]
\begin{itemize}
    \item Cardholders are fully responsible for all transactions made with the card, whether authorized or disputed.
    \item In the event of loss, theft, or unauthorized use, prompt reporting is required to limit liability.
    \item HackMerced Bank is not liable for any losses resulting from the misuse of the card, except where prohibited by law.
\end{itemize}

\vspace{1em}
\textbf{7. Dispute Resolution and Governing Law}\\[1ex]
\begin{itemize}
    \item All disputes arising from the use of this credit card will be subject to binding arbitration in accordance with HackMerced Bank’s policies.
    \item This agreement shall be governed by and construed in accordance with the laws of the jurisdiction in which HackMerced Bank operates.
\end{itemize}

\vspace{1em}
\textbf{8. Amendments and Updates}\\[1ex]
\begin{itemize}
    \item HackMerced Bank reserves the right to modify these Terms and Conditions at any time. Continued use of the card constitutes acceptance of any such modifications.
    \item Cardholders will be notified of major changes via mail or electronic communication.
\end{itemize}

\vspace{1em}
\textbf{9. Data Privacy}\\[1ex]
\begin{itemize}
    \item Personal information collected will be used for credit evaluation, fraud prevention, and regulatory compliance.
    \item HackMerced Bank will handle all data in accordance with applicable data protection laws.
    \item By applying, you consent to the collection, use, and sharing of your personal information as described in the bank’s privacy policy.
\end{itemize}

\vspace{1em}
\textbf{10. Miscellaneous Provisions}\\[1ex]
\begin{itemize}
    \item Additional fees, restrictions, and penalties may apply as detailed in supplementary guidelines provided upon account activation.
    \item In the event of a conflict between promotional materials and this agreement, the terms of this agreement shall prevail.
    \item If any provision of this agreement is found to be invalid or unenforceable, the remaining provisions shall remain in full force and effect.
\end{itemize}
\end{spacing}

\newpage

\section*{Section VI: Benefits Overview}
\subsection*{A. Rewards Program}
\begin{itemize}
    \item \textbf{Earning Points:}
    \begin{itemize}
        \item Earn 3 points per dollar on travel and dining purchases.
        \item Earn 2 points per dollar on everyday purchases.
        \item Additional bonus points for milestone spending achievements.
    \end{itemize}
    \item \textbf{Redemption Options:}
    \begin{itemize}
        \item Points can be redeemed for travel packages, exclusive merchandise, statement credits, or cash back.
        \item Special partner offers may provide enhanced redemption values.
    \end{itemize}
    \item \textbf{Sign-Up Bonus:} Earn 90,000 bonus points after spending \$4,000 on eligible purchases within the first 3 months.
    \item \textbf{Definition of Eligible Purchases:}
    \begin{itemize}
        \item Eligible purchases are defined as transactions made with the Diamond Reserve card for goods or services at the point of sale.
        \item Excludes cash advances, balance transfers, recurring subscription fees, finance charges, and any administrative fees.
        \item Returns, refunds, and promotional credits are not considered eligible unless explicitly stated otherwise.
    \end{itemize}

\end{itemize}

\subsection*{B. Travel Benefits}
\textbf{Overview:} The Diamond Reserve card provides a comprehensive suite of travel benefits designed to enhance every aspect of your journey. These benefits, applicable to both domestic and international travel, are subject to the following detailed terms and conditions.

\begin{enumerate}[label=\arabic*.]
    \item \textbf{Airport Lounge Access:}
    \begin{itemize}
        \item Enjoy complimentary access to over 1,200 airport lounges worldwide through the exclusive \textit{Prime Pass Lounge} network.
        \item Each cardholder is entitled to access for themselves and one guest per visit; additional guests may be admitted at a nominal fee of \$25 per person.
        \item Access is subject to lounge capacity, and some lounges may require advance enrollment or reservation through the dedicated lounge portal.
    \end{itemize}
    \item \textbf{Travel Insurance:}
    \begin{itemize}
        \item \textbf{Trip Cancellation and Interruption:} Receive coverage up to \$15,000 per insured event if a trip is canceled or interrupted due to unforeseen circumstances such as severe weather, sudden illness, or mechanical failures.
        \item \textbf{Baggage Loss and Delay:} Obtain reimbursement up to \$2,500 for lost, stolen, or delayed baggage per incident, provided you submit the necessary documentation within 48 hours of the occurrence.
        \item \textbf{Emergency Medical Coverage:} Benefit from emergency medical expense coverage up to \$75,000 per trip when traveling abroad, with pre-authorization required for expenses exceeding \$5,000.
        \item \textbf{Accidental Death and Dismemberment:} In the event of accidental death or dismemberment during travel, receive benefits up to \$100,000, subject to policy conditions and exclusions.
        \item All travel insurance benefits are subject to annual limits, deductibles, and other restrictions detailed in the supplemental insurance policy.
    \end{itemize}
    \item \textbf{Foreign Transaction Fee Waiver:}
    \begin{itemize}
        \item No foreign transaction fees are applied on purchases made in any foreign currency.
        \item Standard currency conversion fees imposed by payment networks may still apply; however, these are capped at a maximum of 2\% per transaction.
    \end{itemize}
    \item \textbf{Global Concierge Services:}
    \begin{itemize}
        \item Enjoy 24/7 access to a dedicated concierge service for booking flights, hotel accommodations, restaurant reservations, and event planning.
        \item The concierge team, operating under the moniker \textit{TravelGenie Assist}, provides personalized travel recommendations and custom itinerary planning.
        \item Response times and service availability may vary based on your destination and the time of inquiry.
    \end{itemize}
    \item \textbf{Travel Upgrades and Exclusive Offers:}
    \begin{itemize}
        \item Benefit from priority check-in, complimentary seat upgrades, and exclusive deals at over 500 partner hotels and airlines globally.
        \item Pre-approved discounts and special offers are available exclusively for Diamond Reserve cardholders through the \textit{Elite Traveler Club}.
        \item Terms and availability of these offers are subject to change without prior notice and may require additional verification.
    \end{itemize}
\end{enumerate}

\subsection*{C. Purchase Protection \& Extended Warranties}
\begin{itemize}
    \item \textbf{Extended Warranty:} 
    \begin{itemize}
        \item Eligible purchases made with the Diamond Reserve card receive an automatic extended warranty that adds up to 24 months beyond the manufacturer’s original warranty.
        \item The extended warranty covers defects in materials and workmanship under normal use, subject to exclusions detailed in the warranty policy.
        \item Claims must be filed within the warranty period and accompanied by proof of purchase and documentation from the original manufacturer.
    \end{itemize}
    
    \item \textbf{Price Protection:} 
    \begin{itemize}
        \item If an identical item is discovered at a lower advertised price by a recognized retailer within 60 days of purchase, cardholders may request a price adjustment.
        \item To qualify, the lower price must be verifiable through an official website or printed advertisement and be available for sale to the general public.
        \item The price protection benefit is subject to a maximum reimbursement limit of \$250 per item, and exclusions apply for clearance or refurbished items.
    \end{itemize}
    
    \item \textbf{Fraud Protection:} 
    \begin{itemize}
        \item Cardholders benefit from zero liability for any unauthorized transactions, provided that such transactions are reported within 24 hours of detection.
        \item In the event of fraudulent activity, the cardholder is only responsible for any charges incurred up to a maximum of \$50 until the matter is resolved.
        \item The bank reserves the right to investigate and determine the legitimacy of each claim, and in cases of negligence or delayed reporting, standard liability rules may apply.
    \end{itemize}
\end{itemize}

\subsection*{D. Digital and Financial Management Tools}
\begin{itemize}
    \item \textbf{Real-Time Alerts:}
    \begin{itemize}
        \item Receive instant notifications for all account activity including purchases, payment reminders, and potential security alerts.
        \item Customizable alert settings allow you to choose which types of transactions trigger notifications.
        \item Alerts can be delivered via SMS, email, or push notifications through the dedicated mobile app.
    \end{itemize}
    
    \item \textbf{Online and Mobile Access:}
    \begin{itemize}
        \item Secure, 24/7 access to your account through both the HackMerced Bank website and mobile application.
        \item Features include bill payment, balance monitoring, transaction history, and customizable budgeting tools.
        \item Integrated financial planning resources allow for expense tracking, goal setting, and interactive financial insights.
        \item Multi-factor authentication and biometric logins ensure enhanced security for all digital transactions.
    \end{itemize}
    
    \item \textbf{Credit Monitoring:}
    \begin{itemize}
        \item Complimentary credit score monitoring provided on a monthly basis, with detailed analysis of credit trends.
        \item Receive alerts about significant changes to your credit report, helping you stay proactive against fraud or identity theft.
        \item Personalized financial insights and recommendations are offered based on your credit performance and spending habits.
        \item Secure access to a comprehensive credit dashboard to review and manage your credit health.
    \end{itemize}
\end{itemize}

\subsection*{E. Premium Customer Support}
\begin{itemize}
    \item \textbf{Dedicated Support Line:}
    \begin{itemize}
        \item Access a dedicated customer support hotline exclusively for Diamond Reserve cardholders, available 24/7.
        \item Priority handling for inquiries, disputes, and technical issues with guaranteed response times under 30 minutes.
        \item Support staff are specially trained to handle high-priority cases and to provide personalized assistance for account-related issues.
    \end{itemize}
    
    \item \textbf{Personal Financial Consultations:}
    \begin{itemize}
        \item Benefit from personalized financial consultations with certified financial advisors at no additional cost.
        \item Consultations cover budgeting, investment strategies, debt management, and long-term financial planning.
        \item Appointments can be scheduled online or via the dedicated customer support hotline, with both virtual and in-person options available.
        \item Regular financial reviews are provided to help optimize your credit usage and overall financial health.
    \end{itemize}
\end{itemize}

\subsection*{F. Additional Perks}
\begin{itemize}
    \item \textbf{Exclusive Discounts:}
    \begin{itemize}
        \item Enjoy special offers and discounts at over 300 partner merchants worldwide, including dining, retail, and entertainment venues.
        \item Discounts may include up to 20\% off purchases, cashback incentives, or exclusive bundle offers.
        \item Offers are updated monthly and are accessible via the HackMerced Bank mobile app and website.
    \end{itemize}
    
    \item \textbf{Access to Private Events:}
    \begin{itemize}
        \item Receive invitations to exclusive events such as private concerts, gourmet dining experiences, and high-profile sports events.
        \item Enjoy pre-sale ticket opportunities for concerts, theater shows, and special exhibitions under the \textit{Elite Access Pass} program.
        \item Participation may require RSVP and is subject to availability; some events may have a nominal service fee for VIP arrangements.
    \end{itemize}
    
    \item \textbf{Loyalty Bonuses:}
    \begin{itemize}
        \item Earn periodic loyalty rewards based on cumulative spending and account activity.
        \item Bonus points are awarded during milestone achievements, anniversaries of account activation, and special promotional periods.
        \item Loyalty bonuses can be redeemed for additional travel rewards, merchandise, or statement credits, as per the \textit{Elite Traveler Club} terms.
    \end{itemize}
\end{itemize}

\newpage

\section*{Section VII: Electronic Signature}
By typing your full name below, you acknowledge that you have read, understood, and agree to all the terms, conditions, and benefits outlined in this application.

\bigskip
\noindent\textbf{Applicant’s Full Name:} Bill Zhang \\[1ex]
\noindent\textbf{Date (MM/DD/YYYY):}  \\[1ex]
\noindent\textbf{Electronic Signature:}  \\[1ex]

\vspace{2cm}
\noindent\rule{\textwidth}{0.4pt}\\
\textit{For Office Use Only}\\[1ex]
\textbf{Application Reviewed By:} \underline{\hspace{3in}}\\[2ex]
\textbf{Review Date:} \underline{\hspace{2in}}\\[2ex]
\textbf{Approval Code:} \underline{\hspace{2in}}

\bigskip

\noindent\textbf{\textit{Disclaimer:}} This application form is entirely fictitious and created solely for demonstration purposes. It does not represent a real financial product or offer from HackMerced Bank.
 
\end{document}
